\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.25in]{geometry}
\usepackage{enumerate}
\usepackage{microtype}

\begin{document}
\vspace*{\fill}
	\begin{center}
		\begin{Huge}
				\textbf {CNS - OSPE}
		\end{Huge}	
	\end{center}

	\begin{enumerate}[I]
		\item \textbf{Test the position sense in the upper limb of the given subject.}
		\begin{enumerate}[1]
			\item Make the subject sit comfortably and stand on the right side.
			\item Give instruction about the flexed and extended position of the index finger and ask the subject to imitate the same movement on the opposite limb.
			\item Ask the subject to close his eyes. Stabilize the index finger at the sides of the distal interphalangeal joint.
			\item Do the passive flexion and extension of the distal phalanx of the index finger and report.
		\end{enumerate}
		
		\item \textbf{Test the tone of the upper limb muscles at the elbow joint in the given subject.}


		\begin{enumerate}[1]
			\item Make the subject comfortable and stand on the right side of the subject.
			\item Expose the part to be examined. Feel the Tautness of the muscle by holding the muscle to be examined between the thumb and other four fingers.
			\item Feel the tone of the muscle by performing passive movements.
			\item Do the same on the other limb and report.
		\end{enumerate}				
		
		\item \textbf{Test the power of the biceps muscle in the given subject}
		\begin{enumerate}[1]
		\item Make the subject comfortable and stand on the right side of the subject.
		\item Expose the part to be examined and instruct the patient about the flexion movement and application of resistance.
		\item Ask the subject to flex the arm against resistance and feel the strength of the biceps muscle.
		\item Do the same on the other limb and report.
		\end{enumerate}
		
		\item \textbf{Test the coordination of movement in the upper limb by the finger finger nose test in the given subject.}
		\begin{enumerate}[1]
		\item Make the subject comfortable and stand on the right side.
		\item Ask the subject to extend one arm on the side and put your index finger in front of the subject.
		\item Ask the subject to first touch your finger with his index finger and then touch his nose 2 to 3 times.
		\item Do the same procedure on the other limb and report.
		\end{enumerate}
		
		\item \textbf{Demonstrate the Rinne’s test in the given subject.}
		\begin{enumerate}[1]
		\item Make the subject comfortable and give the instruction.
		\item Vibrate the tuning fork and keep the base over the mastoid process behind the ear.
		\item Ask the subject to raise a finger when he stops hearing the sound, immediately hold the prongs of the tuning fork parallel to the external ear and ask whether  he can hear the sound.
		\item Do the same on the other side and report	
		\end{enumerate}
		
		\item \textbf{Elicit the Knee jerk in the given subject in the sitting posture.}
		\begin{enumerate}[1]
		\item To stand on the right side of the subject. Proper positioning of the subject -- he must cross the leg \& the leg should not touch the ground.
		\item Proper holding of the knee hammer.
		\item Strike the patellar tendon with the narrow end of the knee hammer (only wrist movement)
		\item Elicit the reflex similarly on the opposite side and report.
		\end{enumerate}
		
		\item \textbf{Examine the Plantar reflex in the given subject}
		\begin{enumerate}[1]
		\item To stand on the right side of the subject. Instruct the subject to stretch the leg on the stool \& to relax completely.
		\item Gently fix the foot by placing the left hand a little above the ankle.
		\item Gently stroke with the pointed metallic end of the Knee hammer on the outer edge of the sole of the foot from heel towards the little toe \& then medially across the Metatarsals.
		\item Elicit the reflex on the other limb and report.
		\end{enumerate}
	\end{enumerate}
\vspace*{\fill}

\newpage
%\vspace*{\fill}
	\begin{center}
		\begin{Huge}
				\textbf {CVS \& RS -- OSPE}
		\end{Huge}	
	\end{center}
\begin{enumerate}[I]
\item \textbf{Examine the JVP of the given subject.}
	\begin{enumerate}[1]
		\item Make the subject to sit with the upper part of the body supported at an angle of 45 degree.
		\item The chin is turned slightly to the left.
		\item Inspect the neck veins carefully.
		\item Report.
	\end{enumerate}
	
\item \textbf{Examine the movements of the chest wall of the given subject.}
	\begin{enumerate}[1]
	\item Make the subject sit comfortably and stand on front.
	\item Place the palm over the chest on both sides with fingers spread apart and the thumbs approximating each other in the midline.
	\item Ask the subject to take in a deep inspiration.
	\item Observe the separation of the thumb with the movements of the chest wall during deep inspiration and report.
	\end{enumerate}

\item \textbf{Examine the heart sounds of the given subject}
	\begin{enumerate}
	\item Make the subject comfortable and stand to the subject’s right side.
	\item Expose the chest, touch and show all the four auscultatory areas.
	\item Place the diaphragm of the stethoscope over all the 4 areas and auscultate.
	\item Report. 
	\end{enumerate}

\end{enumerate}
%\vspace*{\fill}

\end{document}